Addition and removal energies of circular quantum dots

### 2017-04-30 Manuscript/paper.tex
Add more data and fits
Fit data is now at Datafiles/fit_data.*.txt which has a simpler format
(without all the "best_*" columns, which actually caused a few cases to
be missing whenever there's only 1 data point for a particular system).

Not all cases are solvable with our selection many-body methods.  Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.  Cases where the methods required more than our allocated time to arrive at a result are marked ``n.c.'' (``no convergence'').  For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').  Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.

>>>>

Not all cases are solvable with our selection many-body methods.  Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.  Cases where IM-SRG converged too slowly to be feasible or diverged are marked ``n.c.(I)''.  For the extrapolations in Section \ref{subsec:extrapolation}, some fits could not be done due to missing data caused by IM-SRG(2) or CCSD nonconvergence (``n.c.''); others converged but resulted in unphysical $\beta \le 0$ (``n.f.'').  Cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
